\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}

\definecolor{accent}{HTML}{2C3E50}
\hypersetup{colorlinks=true, urlcolor=accent}
\pagestyle{empty}

\begin{document}

% Header
\begin{flushleft}
{\large\bfseries Nidhi Shetty} \\[4pt]
+44 7368 215147 \\
\href{mailto:nidhishettyuk23@gmail.com}{nidhishettyuk23@gmail.com} \\
\href{https://www.linkedin.com/in/nidhi-shetty23-1841b7181}{linkedin.com/in/nidhi-shetty23} \\[16pt]
\today
\end{flushleft}

\vspace{8pt}

Dear Hiring Manager,

\vspace{6pt}

I am writing to apply for the \textbf{[Role Title]} position at \textbf{[Company Name]}. With hands-on experience in prime brokerage settlement, trade lifecycle management, and risk operations at Morgan Stanley, I am confident in my ability to contribute to your team from day one.

\vspace{6pt}

\textbf{What I bring:}

\vspace{2pt}

At Morgan Stanley's Prime Brokerage in Glasgow, I managed pre-matching and settlement of fixed income and equity trades across US, EMEA, and APAC markets for hedge fund and institutional clients. My key contributions included:

\begin{itemize}
    \setlength{\itemsep}{4pt}
    \item Improving Straight-Through Processing (STP) rates by 10\% by building Python and Excel reconciliation tools that auto-flagged mismatches before settlement deadlines.
    \item Resolving complex settlement failures involving tri-party repos and cross-border custody transfers, reducing average resolution time from 3 days to same-day for priority clients.
    \item Monitoring post-trade exceptions and escalating market and regulatory risks, ensuring compliance with CSDR and T+1 settlement requirements.
\end{itemize}

\vspace{4pt}

\textbf{Why this role:}

\vspace{2pt}

[1--2 sentences on why this specific role and company appeal to you. Reference something specific from the job description or the company's business that connects to your experience.]

\vspace{6pt}

\textbf{Technical skills:}

\vspace{2pt}

I am proficient in advanced Excel (VBA, Power Query, Pivot Tables), Bloomberg Terminal, CTM, and Refinitiv Eikon, with additional experience in Python (pandas, numpy, automation scripting) and AI-assisted development (Claude, ChatGPT, Copilot). I hold an MSc in Investment and Risk Finance (Distinction) from the University of Westminster, with coursework in financial modelling, portfolio management, and risk management.

\vspace{6pt}

I would welcome the opportunity to discuss how my experience aligns with your team's needs. I am available for a conversation at your convenience.

\vspace{12pt}

Kind regards, \\[4pt]
\textbf{Nidhi Shetty}

\end{document}
