\documentclass[11pt,a4paper]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{mdframed}
\usepackage{verbatim}

\definecolor{primary}{HTML}{2C3E50}
\definecolor{accent}{HTML}{34495E}
\definecolor{green}{HTML}{27AE60}
\definecolor{red}{HTML}{E74C3C}
\definecolor{lightgray}{HTML}{F5F5F5}
\hypersetup{colorlinks=true, urlcolor=accent}
\pagestyle{empty}

\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{14pt}{6pt}

\titleformat{\subsection}{\normalsize\bfseries\color{accent}}{}{0em}{}
\titlespacing{\subsection}{0pt}{10pt}{4pt}

\newmdenv[backgroundcolor=lightgray, linewidth=0pt, innerleftmargin=10pt, innerrightmargin=10pt, innertopmargin=8pt, innerbottommargin=8pt]{copybox}

\begin{document}

{\LARGE\bfseries\color{primary} LinkedIn Profile Makeover}\\[4pt]
{\large Nidhi Shetty --- Step-by-Step Instructions}\\[4pt]
{\small Total time: \textasciitilde25 minutes. Do this BEFORE applying to any roles.}

\vspace{6pt}
\begin{mdframed}[linecolor=red, linewidth=1pt, innerleftmargin=10pt, innerrightmargin=10pt, innertopmargin=8pt, innerbottommargin=8pt]
\textcolor{red}{\bfseries IMPORTANT: STEALTH MODE}\\[2pt]
All changes below are designed so your current employer (Here and Now 365) will NOT know you are job searching. We avoid: ``Open to Work'' badge, explicit ``looking for roles'' language, and anything that signals departure. The changes look like a normal profile polish --- not a job search.
\end{mdframed}

\vspace{8pt}

%% ============================================================
\section{What's Good (Keep As-Is)}

\begin{itemize}[leftmargin=1.2em]
    \item \textcolor{green}{\bfseries Profile photo} --- professional, friendly, good quality
    \item \textcolor{green}{\bfseries Banner image} --- London finance skyline, works perfectly
    \item \textcolor{green}{\bfseries 500+ connections} --- solid network
    \item \textcolor{green}{\bfseries Education section} --- well filled out (Westminster + Mumbai)
    \item \textcolor{green}{\bfseries Morgan Stanley listed} --- has description and skills tagged
    \item \textcolor{green}{\bfseries Bright Network internship} --- with description
    \item \textcolor{green}{\bfseries Python certification} (Udemy) --- validates the Python claim
\end{itemize}

%% ============================================================
\section{Step 1: Change Headline (1 minute) --- HIGHEST IMPACT}

\subsection{Current (PROBLEM):}
{\small\textit{``Finance \& Accounting Professional | Budget Optimisation \& Risk Management | MSc Investment \& Risk Finance | Account Manager''}}

\textcolor{red}{\bfseries Why it's bad:} Too generic. ``Account Manager'' signals advertising. No mention of prime brokerage, trade support, settlement, Python, or Bloomberg --- the exact keywords recruiters search for.

\subsection{Change to:}
\begin{copybox}
Account Manager | Ex-Morgan Stanley Prime Brokerage | MSc Investment \& Risk Finance | Python | Bloomberg
\end{copybox}

{\small\textbf{Why this works:} Keeps your current job title visible (so employer sees nothing suspicious) while stuffing the keywords recruiters actually search for --- ``Morgan Stanley'', ``Prime Brokerage'', ``Python'', ``Bloomberg''. A finance recruiter searching for prime brokerage candidates will find you. Your employer sees a normal profile headline that mentions your current role.}

\textbf{How:} Click the pencil icon next to your name $\rightarrow$ Edit ``Headline'' field $\rightarrow$ Paste the text above $\rightarrow$ Save.

%% ============================================================
\section{Step 2: Rewrite About Section (5 minutes)}

\subsection{Current (PROBLEM):}
{\small\textit{``As an MSc Investment and Risk Finance graduate... four years of diverse experience across accounting, finance, operations, administration, and customer service...''}}

\textcolor{red}{\bfseries Why it's bad:} Mentions ``customer service'' and ``administration''. Doesn't name Morgan Stanley, Python, STP, or any specific operational keywords that recruiters filter for.

\subsection{Replace entire About section with:}
\begin{copybox}
Operations and finance professional with hands-on experience in prime brokerage settlement, fixed income and equity trade lifecycle, and risk management at Morgan Stanley. Currently applying AI-driven automation and data analytics to improve operational workflows in account management.

Key expertise:\\
--- Pre-matching \& settlement of fixed income and equity trades (US, EMEA, APAC)\\
--- Straight-Through Processing (STP) optimisation --- improved rates by 10\%\\
--- AI-powered automation (Claude, Perplexity, Python) for reconciliation, reporting, and workflow efficiency\\
--- Bloomberg Terminal, Refinitiv Eikon, SafeGUI, CTM\\
--- CSDR compliance, T+1 settlement, risk escalation

Technical: AI Automation (Claude, Perplexity) | Python (pandas, numpy) | Excel (VBA, Power Query) | Bloomberg | SQL | Financial Modelling

MSc Investment and Risk Finance (Distinction) --- University of Westminster
\end{copybox}

{\small\textbf{Note:} This positions you as someone who combines finance domain expertise with modern AI tools --- a rare and highly sought-after combination. Your employer sees someone ``updating their profile with new skills'' (which is normal), not someone job searching. Meanwhile, finance recruiters see AI + prime brokerage + Python --- a killer combination for 2026 ops roles.}

\textbf{How:} Profile $\rightarrow$ ``About'' section $\rightarrow$ Click pencil icon $\rightarrow$ Delete all $\rightarrow$ Paste above $\rightarrow$ Save.

%% ============================================================
\section{Step 3: Remove Two Experiences (2 minutes)}

Delete these --- they add no finance value and actively hurt positioning:

\begin{itemize}[leftmargin=1.2em]
    \item \textcolor{red}{\bfseries Customer Service Assistant --- Simply Fresh} (Jan 2022 -- Dec 2022)\\
    {\small Retail role. Irrelevant. Remove completely.}
    \item \textcolor{red}{\bfseries Administrator --- NHS COVID 19 CLINIC} (Mar 2021 -- Dec 2021)\\
    {\small Admin role during COVID. Already removed from resume. Remove from LinkedIn too.}
\end{itemize}

\textbf{How:} Profile $\rightarrow$ Experience section $\rightarrow$ Click the role $\rightarrow$ Click pencil icon $\rightarrow$ ``Delete experience'' at the bottom.

%% ============================================================
\section{Step 4: Update Morgan Stanley Description (5 minutes)}

Keep the job title (``Financial Operations Analyst'') but \textbf{replace the description} with:

\begin{copybox}
--- Managed pre-matching and settlement of fixed income and equity trades across US, EMEA, and APAC markets for hedge fund and institutional clients, processing \$10M+ in daily trade volume\\
--- Improved Straight-Through Processing (STP) rates by 10\% by building Python and Excel reconciliation tools that auto-flagged mismatches before settlement deadlines\\
--- Identified recurring break patterns across trade data through automated exception monitoring, enabling proactive resolution and reducing average time from 3 days to same-day for priority clients\\
--- Monitored post-trade exceptions in TM and SafeGUI, building automated alerts to surface anomalies and reduce incident occurrences by 15\% quarter-over-quarter\\
--- Ensured compliance with CSDR and T+1 settlement requirements; coordinated with compliance and legal teams on regulatory changes affecting settlement workflows

Skills: Prime Brokerage, Fixed Income Settlement, Equity Settlement, Python, STP, Bloomberg, SafeGUI, CTM, Risk Management, CSDR, Reconciliation, Middle Office Operations
\end{copybox}

\textbf{How:} Experience $\rightarrow$ Morgan Stanley $\rightarrow$ Pencil icon $\rightarrow$ Replace description $\rightarrow$ Save.

%% ============================================================
\section{Step 5: Add Description to Here and Now 365 (3 minutes)}

Currently blank. \textbf{Add:}

\begin{copybox}
--- Automated campaign metric extraction and reporting using AI tools (Claude, Perplexity) and Python, reducing manual reporting time from 4 hours to 45 minutes per campaign cycle\\
--- Built AI-powered workflows using Claude to generate post-campaign analysis, summarise performance data, and draft client-ready insights at scale\\
--- Used Perplexity for competitive research and market trend analysis, feeding findings into campaign strategy and budget reallocation decisions\\
--- Led client presentations translating AI-generated analytics into strategic recommendations, growing account revenue through upselling by 20\%\\
--- Managed 8+ concurrent campaigns, using AI assistants to streamline coordination across creative and media teams (scheduling, briefs, status tracking)
\end{copybox}

{\small\textbf{Why this framing works:} Finance firms increasingly want candidates who can use AI to improve operational efficiency. This shows you don't just ``use AI'' casually --- you build workflows, automate repetitive tasks, and deliver measurable results with it. This is directly transferable to trade ops: imagine using Claude to parse settlement exceptions, draft escalation emails, or build reconciliation logic.}

\textbf{How:} Experience $\rightarrow$ Here and Now 365 $\rightarrow$ Pencil icon $\rightarrow$ Add description $\rightarrow$ Save.

%% ============================================================
\section{Step 5b: Update Bright Network Internship}

\textbf{Update the description} to include AI/research angle:

\begin{copybox}
--- Conducted equity research and company valuations using DCF and comparable analysis, gathering data across public filings and market reports\\
--- Built financial models in Excel to evaluate M\&A scenarios in the infrastructure and real assets space\\
--- Synthesised large volumes of industry data into actionable investment recommendations for senior analysts\\
--- Gained exposure to MIRA's global infrastructure portfolio and asset lifecycle management
\end{copybox}

\textbf{How:} Experience $\rightarrow$ Bright Network $\rightarrow$ Pencil icon $\rightarrow$ Replace description $\rightarrow$ Save.

%% ============================================================
\section{Step 5c: Update Bharath Shetty Tax Consultant}

\textbf{Update the description:}

\begin{copybox}
--- Prepared and analysed financial statements for 30+ corporate and individual clients, using Tally ERP and Excel to identify discrepancies and recommend corrective actions\\
--- Managed end-to-end tax filing (corporate, individual, GST), collaborating with senior consultants to optimise strategies and achieve 12-15\% average reduction in client tax burden\\
--- Automated recurring data entry and reconciliation tasks using Excel macros and scripting, reducing manual processing time by 25\%
\end{copybox}

\textbf{How:} Experience $\rightarrow$ Bharath Shetty $\rightarrow$ Pencil icon $\rightarrow$ Replace description $\rightarrow$ Save.

%% ============================================================
\section{Step 6: DO NOT Enable ``Open to Work''}

\begin{mdframed}[linecolor=red, linewidth=1pt, innerleftmargin=10pt, innerrightmargin=10pt, innertopmargin=8pt, innerbottommargin=8pt]
\textcolor{red}{\bfseries SKIP THIS STEP.} Do NOT turn on ``Open to Work'' --- even the ``Recruiters only'' setting is not fully private. LinkedIn's algorithm is imperfect, and there have been cases where colleagues or managers see the green badge or get notified. It's not worth the risk.

\vspace{6pt}
\textbf{Instead, do this:}
\begin{itemize}[leftmargin=1.2em]
    \item Apply directly to roles using the 25 links we've prepared
    \item Message recruiters privately (Alexander Ashton, Martin Parkinson, Kirsty Toerien)
    \item Let your headline and About section do the passive work --- finance recruiters searching for ``prime brokerage'' or ``Python Bloomberg'' will find you without the badge
\end{itemize}
\end{mdframed}

%% ============================================================
\section{Step 7: Add Skills to Each Experience + Profile (10 minutes)}

LinkedIn lets you tag skills to each experience AND to your overall profile. This is how recruiters find you. Add the following:

\subsection{Profile-level skills (add all of these to your main Skills section):}

\begin{copybox}
\textbf{AI \& Automation:}\\
--- AI Automation\\
--- Claude (Anthropic)\\
--- Prompt Engineering\\
--- Perplexity AI\\
--- AI-Assisted Research\\
--- Workflow Automation\\
\\
\textbf{Finance \& Operations:}\\
--- Prime Brokerage\\
--- Trade Settlement\\
--- Fixed Income\\
--- Equity Trading\\
--- Straight-Through Processing (STP)\\
--- Reconciliation\\
--- Risk Management\\
--- Middle Office Operations\\
--- Trade Lifecycle Management\\
--- CSDR Compliance\\
--- Corporate Actions\\
--- Margin Calls\\
--- Financial Modelling\\
--- Financial Analysis\\
\\
\textbf{Technical:}\\
--- Python (Programming Language)\\
--- pandas\\
--- Bloomberg Terminal\\
--- Refinitiv Eikon\\
--- Microsoft Excel\\
--- VBA\\
--- Power Query\\
--- SQL\\
--- Data Analysis\\
--- SafeGUI\\
--- CTM (Central Trade Manager)\\
\\
\textbf{Soft Skills:}\\
--- Stakeholder Management\\
--- Client Relationship Management\\
--- Cross-functional Collaboration\\
--- Problem Solving\\
--- Analytical Skills
\end{copybox}

\textbf{How:} Profile $\rightarrow$ Skills section $\rightarrow$ ``Add a skill'' $\rightarrow$ Search and add each one. Pin the top 3 most relevant (AI Automation, Prime Brokerage, Trade Settlement).

\subsection{Skills tagged to Morgan Stanley:}

When editing your Morgan Stanley experience, LinkedIn shows ``Skills'' at the bottom. Tag these:

\begin{copybox}
Prime Brokerage, Trade Settlement, Fixed Income, Equity Trading, STP, Reconciliation, Risk Management, Python, Bloomberg Terminal, SafeGUI, CTM, CSDR Compliance, Margin Calls, Corporate Actions, Stakeholder Management, Middle Office Operations, Automation
\end{copybox}

\subsection{Skills tagged to Here and Now 365:}

\begin{copybox}
AI Automation, Claude (Anthropic), Perplexity AI, Prompt Engineering, Python, Data Analysis, Workflow Automation, Campaign Analytics, Client Relationship Management, Stakeholder Management, Statistical Modelling, Cross-functional Collaboration
\end{copybox}

\subsection{Skills tagged to Bright Network Internship:}

\begin{copybox}
Investment Banking, Financial Modelling, Equity Research, DCF Valuation, M\&A Analysis, Financial Analysis, Microsoft Excel, Asset Management, Portfolio Management
\end{copybox}

\subsection{Skills tagged to Bharath Shetty Tax Consultant:}

\begin{copybox}
Financial Analysis, Tax Planning, GST, Financial Statements, Microsoft Excel, VBA, Reconciliation, Accounting, Client Advisory, Regulatory Compliance
\end{copybox}

\vspace{6pt}
{\small\textbf{Why this matters:} LinkedIn's algorithm matches candidates to job postings based on skills. If a recruiter searches ``Prime Brokerage AI Python London,'' you only appear if those exact skills are on your profile. The more tagged skills that match job descriptions, the higher you rank in recruiter search results.}

%% ============================================================
\section{Step 8: Add Missing Certifications (5 minutes)}

Your resume lists certifications not on LinkedIn. Add these:

\begin{itemize}[leftmargin=1.2em]
    \item Bloomberg Essentials
    \item Complete Financial Analyst Course
    \item Introduction to Derivatives
    \item Company Valuation \& Financial Modeling
    \item Fundamentals of Credit
    \item Economics for Capital Markets
\end{itemize}

\textbf{How:} Profile $\rightarrow$ ``Add profile section'' $\rightarrow$ ``Licenses \& certifications'' $\rightarrow$ Add each one.

%% ============================================================
\section{Step 8 (Optional but be careful): Activity}

Your profile currently shows ``No recent posts.'' This isn't a blocker, but to look more active:

\begin{itemize}[leftmargin=1.2em]
    \item Repost 1--2 finance/markets articles per week (general market news, not ``career tips'' or ``job search'' content)
    \item Like or react to posts from finance professionals in your network
    \item \textbf{Do NOT:} Follow company career pages (Goldman Sachs Careers, JP Morgan Jobs, etc.) --- these show up in your activity feed and signal job searching
    \item \textbf{Do NOT:} Post anything about ``new beginnings'', ``open to opportunities'', or career transitions
    \item \textbf{Safe to follow:} Bloomberg News, Financial Times, Reuters --- these look like professional development, not job hunting
\end{itemize}

%% ============================================================
\section{Privacy Settings to Check}

Before making any changes, ensure these LinkedIn privacy settings are configured:

\begin{enumerate}[leftmargin=1.5em]
    \item \textbf{Settings $\rightarrow$ Visibility $\rightarrow$ ``Share profile updates with your network''} $\rightarrow$ Turn \textbf{OFF}\\
    {\small This prevents LinkedIn from broadcasting ``Nidhi updated her profile!'' to your connections (including colleagues).}
    \item \textbf{Settings $\rightarrow$ Visibility $\rightarrow$ ``Notify connections when you're in the news''} $\rightarrow$ Turn \textbf{OFF}
    \item \textbf{Settings $\rightarrow$ Privacy $\rightarrow$ ``Profile viewing options''} $\rightarrow$ Set to \textbf{Private mode}\\
    {\small So when you view Goldman Sachs or JP Morgan recruiter profiles, they won't see your name.}
    \item \textbf{Settings $\rightarrow$ Privacy $\rightarrow$ ``Active status''} $\rightarrow$ Turn \textbf{OFF}\\
    {\small Hides when you're online --- so colleagues don't see you browsing LinkedIn at odd hours.}
\end{enumerate}

\textbf{Do these FIRST, before making any profile edits.}

%% ============================================================
\section{Verification After Changes}

Once all changes are made, test by:

\begin{enumerate}[leftmargin=1.5em]
    \item Open a private/incognito browser window (NOT logged in)
    \item Search Google for: \texttt{site:linkedin.com ``Nidhi Shetty'' prime brokerage}
    \item Your profile should appear with the new headline
    \item Log back in and search LinkedIn for: \texttt{``Prime Brokerage Python Bloomberg London''}
    \item Your profile should appear within the first few pages of results
    \item Check your activity feed --- make sure no ``profile update'' notifications were sent
\end{enumerate}

\vspace{12pt}
\begin{center}
\textcolor{primary}{\rule{0.5\textwidth}{0.5pt}}\\[8pt]
{\small\textit{After completing these steps, proceed to apply to all 25 roles.}}
\end{center}

\end{document}
