\documentclass[11pt,a4paper]{article}

% Packages
\usepackage[margin=0.7in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}

% Colors
\definecolor{primary}{HTML}{2C3E50}
\definecolor{accent}{HTML}{34495E}

% Formatting
\titleformat{\section}{\large\bfseries\color{primary}}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}
\setlist[itemize]{leftmargin=1.2em, itemsep=2pt, parsep=0pt, topsep=3pt}
\hypersetup{colorlinks=true, linkcolor=accent, urlcolor=accent}
\pagestyle{empty}

\begin{document}

% Header
\begin{center}
    {\LARGE\bfseries NIDHI SHETTY} \\[6pt]
    +44 7368 215147 \enspace$\vert$\enspace
    \href{mailto:nidhishettyuk23@gmail.com}{nidhishettyuk23@gmail.com} \enspace$\vert$\enspace
    \href{https://www.linkedin.com/in/nidhi-shetty23-1841b7181}{linkedin.com/in/nidhi-shetty23}
\end{center}

% Profile
\section{Profile}
Operations and finance professional with hands-on experience in prime brokerage settlement, fixed income and equity trade lifecycle, and risk management at Morgan Stanley. Combines quantitative analysis skills with Python-driven automation and Bloomberg terminal proficiency to improve operational efficiency across global markets. Looking to leverage this experience in an investment banking or institutional finance environment where trade operations expertise and analytical capabilities drive measurable impact.

% Key Achievements
\section{Key Achievements}
\begin{itemize}
    \item Improved Straight-Through Processing (STP) rates by 10\% at Morgan Stanley by building Python/Excel reconciliation tools that auto-flagged mismatches before settlement deadlines.
    \item Managed pre-matching and settlement of fixed income and equity trades across US, EMEA, and APAC markets, processing \$10M+ in daily volume for institutional clients.
    \item Built financial models in Python and Excel to evaluate M\&A scenarios during investment banking internship at Bright Network.
\end{itemize}

% Experience
\section{Experience}

\textbf{Advertising Account Manager} \hfill May 2024 -- Present \\
\textit{Here and Now 365, London}
\begin{itemize}
    \item Built Python scripts to automate campaign metric extraction from platform APIs, reducing manual reporting time from 4 hours to 45 minutes per campaign cycle.
    \item Delivered post-campaign analysis using statistical modelling to isolate channel-level ROI, directly informing budget reallocation that improved next-quarter campaign performance by 15\%.
    \item Led client presentations translating complex data into strategic recommendations, growing account revenue through upselling by 20\%.
    \item Coordinated cross-functional delivery across creative and media teams, managing timelines and dependencies for 8+ concurrent campaigns.
\end{itemize}

\textbf{Operations Analyst, Prime Brokerage} \hfill Jan 2023 -- Apr 2024 \\
\textit{Morgan Stanley, Glasgow}
\begin{itemize}
    \item Managed pre-matching and settlement of fixed income and equity trades across US, EMEA, and APAC markets for hedge fund and institutional clients, processing \$10M+ in daily trade volume.
    \item Improved Straight-Through Processing (STP) rates by 10\% by identifying recurring break patterns and building Excel/Python reconciliation tools to auto-flag mismatches before settlement deadlines.
    \item Resolved complex settlement failures involving tri-party repos and cross-border custody transfers, reducing average resolution time from 3 days to same-day for priority clients.
    \item Identified and escalated potential market and regulatory risks by monitoring post-trade exceptions in TM and SafeGUI, reducing incident occurrences by 15\% quarter-over-quarter.
    \item Collaborated with account managers and compliance stakeholders to address margin call discrepancies and ensure adherence to CSDR and T+1 settlement requirements.
\end{itemize}

\textbf{Investment Banking \& Asset Management Internship} \hfill Jun 2021 \\
\textit{Bright Network, London}
\begin{itemize}
    \item Conducted equity research and company valuations using DCF and comparable analysis, presenting investment recommendations to senior analysts.
    \item Built financial models in Excel and Python to evaluate M\&A scenarios in the infrastructure and real assets space.
    \item Gained exposure to MIRA's global infrastructure portfolio and asset lifecycle management including acquisition, diversification, and disposal strategies.
\end{itemize}

\textbf{Account Assistant} \hfill Sep 2018 -- Aug 2019 \\
\textit{Bharath Shetty Tax Consultant, Mumbai}
\begin{itemize}
    \item Prepared and analysed financial statements for 30+ corporate and individual clients, using Tally ERP and Excel to identify discrepancies and recommend corrective actions.
    \item Managed end-to-end tax filing (corporate, individual, GST) collaborating with senior consultants to optimise strategies, achieving average client savings of 12--15\% on effective tax burden.
    \item Automated recurring data entry tasks using Python scripts and Excel macros, reducing manual processing time by 25\%.
\end{itemize}

% Education
\section{Education}

\textbf{MSc Investment and Risk Finance} --- \textit{Distinction} \hfill Jan 2021 -- Jun 2022 \\
University of Westminster, London \\
{\small Modules: Modern Portfolio Management, Financial Modelling, International Risk Management, Forecasting \& Market Risk Modelling, Financial Markets \& Institutions} \\
{\small Dissertation: \textit{Do Acquirers Gain Value in Entertainment \& Media Sector Takeover Transactions?}}

\vspace{4pt}
\textbf{Master of Commerce} --- \textit{Merit} \hfill Aug 2017 -- Jan 2019 \\
University of Mumbai \\
{\small Modules: Advanced Financial Accounting, Financial Management, Economics of Global Trade \& Finance}

\vspace{4pt}
\textbf{Bachelor of Commerce} --- \textit{GPA: 5.8/7} \hfill Jun 2013 -- Jan 2017 \\
University of Mumbai

% Skills
\section{Technical Skills}

\begin{tabular}{@{}l p{12cm}@{}}
\textbf{Platforms \& Tools:} & Bloomberg Terminal, Refinitiv Eikon, SafeGUI, TM (Trade Management), MS Office Suite \\[3pt]
\textbf{Programming \& Data:} & Python (pandas, numpy, automation scripts), SQL (basic), Advanced Excel (VBA, Power Query) \\[3pt]
\textbf{Domain Expertise:} & Trade settlement (T+1/T+2), Prime brokerage ops, Fixed income \& equity markets, Risk assessment, CSDR compliance, STP optimisation, Financial modelling \\[3pt]
\textbf{Languages:} & English (fluent), Hindi (fluent), Marathi (fluent), German (basic) \\
\end{tabular}

% Certifications
\section{Certifications}

{\small
\begin{tabular}{@{}l l l@{}}
CITI Virtual Experience Program & Company Valuation \& Financial Modeling & Bloomberg Essentials \\
Complete Financial Analyst Course & Introduction to Derivatives & Fundamentals of Credit \\
Economics for Capital Markets & Introduction to Corporate Finance & Reading Financial Statements \\
\end{tabular}
}

% Interests
\section{Interests}
District-level Dodgeball player \enspace$\cdot$\enspace Taekwondo Black Belt \enspace$\cdot$\enspace Volunteering \enspace$\cdot$\enspace Financial blogs \& market commentary

\end{document}
